Do motif roles provide unique information about species risk of extinction?

### 2021-06-04 manuscript/motifs_vs_degree.tex
trying to sync git to overleaf

    \subsection*{How does mean persistence vary with global network properties?}

        Network average persistence of consumers naturally decrease with increasing level of disturbance of basal resources (Table S1, \emph{Appendix SA}). Network size and connectance also affect persistence, but to a much smaller extent (Figure~\ref{fig:lm_CS}). Persistences generally decrease when networks are more connected, but the effect of network size varies depending on level of disturbance: at low disturbance small and highly-connected webs show the lowest persistence, whereas at high disturbance level large and highly connected webs show the lowest persistence (Fig. S1, \emph{Appendix SA}).

@@

    \subsection*{How do motif profiles vary with global network properties?}

        A network's normalized motif profile (i.e., proportions of the total made up by each motif)
        % ; see \emph{Appendix SX} for non-normalized motif profiles) 
        is related to the network's size, connectance, and the interaction between them ($F_{1,2996}$=74.3, $p$\textless0.001; $F_{1,2996}$=4203, $p$\textless0.001; and $F_{1,2996}$=27.8, $p$\textless0.001, respectively in a PERMANOVA of dissimilarity in normalized network motif profiles against network size, connectance, and their interaction).
        Unequal variation in motif profiles across levels of size, connectance, and their interaction may, however, mean that these PERMANOVA results are false positives (Fig. S2, \emph{Appendix SB}).

        The proportions of apparent competition and three-species chains in a network's motif profile tended to decrease with increasing connectance while the proportion of omnivory increased with increasing connectance (Table S2, \emph{Appendix SB}). 
        Network size and the interaction between network size and connectance did not strongly affect the frequencies of most motifs (Fig.~\ref{motif_proportion_lms}). The proportion of direct competition, however, decreased with increasing connectance in small networks but showed very little change in large webs.

@@

@@

        The motif profile of a network does relate to the mean persistence of consumers ($F_{1,2998}$=571, $p$\textless0.001). Mean persistence is higher in networks with higher proportions of the chain, direct competition, and apparent competition motifs (Table S3, \emph{Appendix SC}). Conversely, mean persistence is lower in networks with higher proportions of the omnivory motif. These trends hold for all levels of disturbance (Table S3, \emph{Appendix SC}). Dispersion of motif profiles varies between networks with different levels of persistence ($F_{134,2865}$=2.19$\times10^{24}$, $p$=\textless0.001). For example, networks with higher persistence have more variable motif profiles ($\beta$=0.183, $p$\textless0.001).

@@

@@

        % See \emph{Appendix SY} for relationships between persistence and non-normalized motif participation.

@@

            At low levels of disturbance, species' persistence increased with increasing proportions of the omnivory and direct competition motifs. Conversely, a species' persistence decreases with increasing proportion of the apparent competition motif. Finally, a species persistance is negatively but not significantly related to the proportion of the three-species chain (Figure~\ref{fig:prop_lmer_all}).

            At high levels of disturbance, a species' persistence decreases with increasing proportion of the three-species chain, but increases with increasing proportion of all other motifs (Figure~\ref{fig:prop_lmer_all}).
            This means that increased disturbance strengthen the effects of the three-species chain motif and changes direction of the effect from the apparent competition motif  (Table S4, \emph{Appendix SD}).
            The effect of omnivory on persistence is still positive but weaker at higher levels of disturbance, and the effect of direct competition are largely unaffected by disturbance level.

@@

            By fitting linear regressions of persistence against motif proportions for the species for each network separately, we can observe how the relationships between motifs and persistence change with the level of disturbance and global network structure. Network size had a much smaller effect than connectance (Fig. S3; \emph{Appendix SE}); we therefore focus on connectance here. 
            Networks with high connectance generally have more consistent relationships between persistence and motif participation, i.e., sharper peaks of the density distributions (Fig.~\ref{fig:density_prop_C}). 
            However, there was an interaction between disturbance and connectance for the direct competition and omnivory motifs.

            At low and medium connectances there is little change in the proportion of positive slopes (\textgreater80\%) for the different levels of disturbance. 
            At high connectances, however, the proportion of positive slopes is lower overall and decreases with increasing disturbance. 
            This means that at low levels of connectance, an increased proportion of the direct competition motif increases persistence in most networks, while the opposite is true with high connectance. 
            The trend is reversed for the omnivory motif.

@@

@@

        Persistence varies with both species in-degree and trophic level (Fig.~\ref{fig:motifs_vs_TL_and_deg}; \emph{Appendix SF}). Increased trophic level is associated with decreasing persistence, although the rate of this decline is slower at higher levels of disturbance (Table S5, \emph{Appendix SF}).
        The interaction between in-degree and disturbance is even stronger, such as having a large number of prey is associated with higher persistence in the no disturbance scenario, but lower persistence at high disturbance.

@@

        Motif participation varied with web size, connectance, and their interaction (Fig. S4, Table S6; \emph{Appendix SG}).
        Species in all networks appeared most frequently in the apparent competition motif, but the frequency of the apparent competition motif decreased with increasing network size and connectance.
        The frequency of the omnivory motif increased sharply with increasing connectance, while the frequency of the direct competition motif increased slightly with increasing network size. 
        Species' motif roles also vary with their in-degree and trophic level (Fig.~\ref{fig:motifs_vs_TL_and_deg}).
        Species with higher in-degree tend to have higher proportions of their motif role made up by omnivory. Proportions of the other three motifs tend to decline with increasing degree.

@@

@@

        \begin{figure}
            \centering
            \includegraphics[width=.95\textwidth]{figures/persistence_positions_byprey.eps}
            \caption{A species' probability of persistence varied with the frequency of different motif positions in its role. Relationships are shown for the range 0-0.8 for all positions, but some positions (especially in the omnivory motif) are less common. Line colour indicates the motif containing a position. Line style indicates the number of prey within the motif for each position. Symbol shape indicates the number of predators within the motif for each position; note that only bottom-up extinctions were included in our simulations. The top set of lines corresponds to a probability of extinction for basal resources of 0.1. The middle set of lines corresponds to a probability of extinction for basal resources of 0.26, and the lowest set of lines corresponds to a probability of extinction for basal resources of 0.5.}
            \label{fig:persistence_positions_prey}
        \end{figure}

@@

        \subsubsection*{Degree and trophic level}

            The top position in the omnivory motif increased with increasing degree across all trophic levels.
            The frequency of the middle position increased with the interaction of degree and trophic level.
            The bottom position was generaly rare, especially for species with high degree or high trophic level (this suggests that the bottom position is frequently a basal resource).

            The frequency of the bottom position in the apparent competition motif decreased strongly with increasing degree, especially for species at a high trophic level.
            The frequency of the top position increased strongly with increasing degree and was not strongly related to trophic level.

            The frequency of the bottom position in the direct competition motif increased with increasing degree, especially for species at a high trophic level.
            The bottom position was very rare, especially for species with high degree (also suggesting that this position is usually a basal resource).

            The bottom position in the three-species chain was generally rare, especially for species with high degree or trophic level (again, this is likely to commonly be basal resources).
            The middle position in the three-species chain did not vary strongly with degree and declined slightly with increasing trophic level.
            The top position in the three-species chain increased with trophic level, degree, and their interaction.

        \subsubsection*{Network size and connectance}

            % Many of these are significant, but the slopes tend to be very shallow. TL and degree are more interesting - this is DEFINITELY SI.
            The frequency of the top position in the apparent competition motif did not vary strongly with network size or connectance.
            The frequency of the bottom position in the apparent competition motif decreased with increasing connectance but did not vary strongly vary with network size.

            The frequency of the top position in the direct competition motif increased slightly with the interaction of network size and connectance (i.e., in large and highly-connected networks).
            The frequency of the bottom position in the direct competition motif was low in all networks.

            The frequency of all three positions in the omnivory motif showed similar relationships with network size and connectance.
            Frequencies of these motifs increased with increasing connectance and were not strongly affected by network size.
            None of the positions in the three-species chain varied strongly with network size or connectance.

>>>>

    \subsection*{How does mean persistence vary with global network structure?}

        Network average persistence of consumers naturally decrease with increasing level of disturbance of basal resources (Table~\ref{tab:per_vs_SC}). Network size and connectance also affect persistence, but to a much smaller extent (Figure~\ref{fig:lm_CS}). Persistences generally decrease when networks are more connected, but the effect of network size varies depending on level of disturbance: at low disturbance small and highly-connected webs show the lowest persistence, whereas at high disturbance level large and highly connected webs show the lowest persistence.

@@

        %\begin{figure}[h!]
        %   \includegraphics[width=0.95\textwidth]{figures/heatmap_CS_BPcompare.eps}
        %    \caption{Heat maps of average consumer persistence in networks with varying connectance (y-axis) and network size (x-axis) at two levels of disturbance to basal resources. Persistence decreases with darker color in the heat map. When basal species are not disturbed, all species experience a baseline extinction risk of $\pi = 0.1$. When basal species are highly disturbed, their baseline extinction risk rises to $\pi = 0.5$ while the baseline risk of consumers is not changed.}
        %    \label{fig:heatmap_CS}
        %\end{figure}

        \begin{table}[hb!]
            \caption{Persistence of consumers within a network depends on network size (S) and connectance (C), the level of disturbance to basal resources (D), and interactions between them. Here we show the effect sizes ($\beta$) and $p$-values for the regression described above. All predictors were centered and scaled before fitting the model. The level of disturbance corresponds to basal resources having a probability of extinction ranging between $0.1 - 0.5$ (see \emph{Methods}).
            }
            \label{tab:per_vs_SC}
            \centering
            \begin{tabular}{c|c c |}
                Predictor & $\beta$ & $p$-value \\
                \hline
                Intercept & 0.572 & \textless0.001 \\
                Size & -5.15$\times10^{-4}$  & \textless0.001 \\
                Connectance & -0.0129 & \textless0.001 \\
                Disturbance & -0.139 & \textless0.001 \\
                S:C & -5.24$\times10^{-4}$ & \textless0.001 \\
                S:D & -3.48$\times10^{-3}$ & \textless0.001 \\
                C:D & -7.00$\times10^{-5}$ & 0.095 \\
                S:C:D: & -2.69$\times10^{-4}$ & \textless0.001 \\
            \end{tabular}
        \end{table}

    \subsection*{How do network motif profile vary with global network properties?}

        A network's normalized motif profile (i.e., proportions of the total made up by each motif; see \emph{Appendix SX} for non-normalized motif profiles) is related to the network's size, connectance, and the interaction between them ($F_{1,2996}$=74.3, $p$\textless0.001; $F_{1,2996}$=4203, $p$\textless0.001; and $F_{1,2996}$=27.8, $p$\textless0.001, respectively in a PERMANOVA of dissimilarity in normalized network motif profiles against network size, connectance, and their interaction).
        The proportions of apparent competition and three-species chains in a network's motif profile tended to decrease with increasing connectance while the proportion of omnivory increased with increasing connectance (Table~\ref{network_prop_lms}). 
        Network size and the interaction between network size and connectance did not strongly affect changes in normalized motif profiles with connectance, except for direct competition (Fig.~\ref{motif_proportion_lms}). The proportion of direct competition decreased with increasing connectance in small networks but showed very little change in large webs.

@@

        \begin{table}[hb!]
            \centering
            \caption{Coefficients for linear regressions relating the proportion of each motif in the total motif profile of a network to network size, connectance, and their interaction. Coefficients in \textbf{bold} are significant (\textless0.05).}
           \label{network_prop_lms}
           \begin{tabular}{c|c c c c c}
                Motif & Intercept & Size & Connectance & Interaction \\
                \hline
                Three-species Chain & \textbf{0.262} & \textbf{1.78$\times10^{-4}$} & \textbf{-0.157} & \textbf{-3.27$\times10^{-3}$} \\
                Apparent Competition & \textbf{0.541} & \textbf{-5.06$\times10^{-4}$} & \textbf{-1.00} & \textbf{2.59$\times10^{-3}$} \\
                Direct Competition & \textbf{0.193} & -3.56$\times10^{-5}$ & \textbf{-0.556} & \textbf{5.92$\times10^{-3}$} \\
                Omnivory & 4.82$\times10^{-3}$ & \textbf{3.64$\times10^{-4}$} & \textbf{1.71} & \textbf{-5.24$\times10^{-3}$}\\
                \hline
                \end{tabular}
        \end{table}

        %However, normalized motif profiles were not homogeneously variable across levels of network size, connectance, or their interaction  ($F_{5,2994}$=16.8, $p$\textless0.001; $F_{4,2995}$=31.7, $p$\textless0.001; and $F_{29,2970}$=11.9, $p$\textless0.001 for ANOVAs of dispersion of motif profiles against size, connectance, and combinations of size and connectance, respectively).These differences in variability can cause false positives in the PERMANOVA test. Variability was highest in small and low-connectance networks (Fig.~\ref{dispersion_normmotifs}).

       % \begin{figure}
        %    \centering
        %    \includegraphics[width=.75\textwidth]{manuscript/figures/proportion_profile_dispersion.pdf}
        %    \caption{Dispersion of normalized motif profiles (i.e., proportions of each motif) within a network about the centroid for that combination of network size and connectance. Each circle represents a single network; circle colour indicates network size. Scatter has been introduced about each level of connectance to increase visual clarity; the levels of connectance we consider are indicated by vertical black lines.}
        %    \label{dispersion_normmotifs}
        %\end{figure}

@@

        The motif profile of a network does relate to the mean persistence of consumers ($F_{1,2998}$=571, $p$\textless0.001). Mean persistence is higher in networks with higher proportions of the chain, direct competition, and apparent competition motifs (Table~\ref{motif_profile_tab}).Conversely, mean persistence is lower in networks with higher proportions of the omnivory motif. These trends hold for all levels of disturbance (Table~\ref{motif_profile_tab}). Dispersion of motif profiles varies between networks with different levels of persistence ($F_{134,2865}$=2.19$\times10^{24}$, $p$=\textless0.001). For example, networks with higher persistence have more variable motif profiles ($\beta$=0.183, $p$\textless0.001).

@@

        \begin{table}[h!]
            \caption{Coefficients ($\beta$) for models relating persistence to the proportion of a network profile, the level of disturbance to basal resources (corresponding to a probability of extinction ranging between 0.1 and 0.5), and their interaction. Predictors were centered and scaled before model fitting. All effects were significant ($p$\textless0.001). We also provide the $R^2$. }
            \label{motif_profile_tab}
            \centering
            \begin{tabular}{c|c c c c c | c}
                Motif & Intercept & Proportion & Disturbance & Interaction & $R^2$\\
                \hline
                Omnivory & 0.572 & -0.0133 & -0.139 & -4.89$\times10^{-4}$ & 0.908 \\
                Apparent competition & 0.572 & 0.0105 & -0.139 & 4.78$\times10^{-4}$ & 0.905 \\
                Direct competition & 0.572 & 2.62$\times10^{-3}$ & -0.139 & 3.84$\times10^{-4}$ & 0.901 \\
                Three-species chain & 0.572 & 6.12$\times10^{-3}$ & -0.139 & -1.90$\times10^{-4}$ & 0.901 \\ 
            \end{tabular}
        \end{table}

@@

        See \emph{Appendix SY} for relationships between persistence and non-normalized motif participation.

@@

            Without disturbance, a species' persistence increases with increasing proportion of the omnivory and direct competition motifs. Conversely, a species' persistence decreases with increasing proportion of the apparent competition motif. Finally, a species persistance is  negatively but not significantly related to the proportion of the three-species chain (Figure~\ref{fig:prop_lmer_all}).

            At high levels of disturbance, a species' persistence decreases with increasing proportion of the three-species chain, but increases with increasing proportion of all other motifs (Figure~\ref{fig:prop_lmer_all}).
            This means that increased disturbance strengthen the effects of the three-species chain motif and changes direction of the effect from the apparent competition motif  (Table~\ref{tab:proportion}).
            The effect of omnivory on persistence is still positive but weaker at higher levels of disturbance, and the effect of direct competition are largely unaffected by disturbance level.

            \begin{table}[hb!]
                \centering
                \caption{Coefficients ($\beta$) and $p$-values ($p$) for models relating persistence to the proportion of a species' role made up by the focal motif, the level of disturbance to basal resources (corresponding to a probability of extinction ranging between 0.1 and 0.5), and their interaction, as well as a random intercept to account for differences in persistence across levels of network size and connectance (Equation~\ref{propreq}). Predictors were centered and scaled before model fitting. We also provide the marginal $R^2_M$ (fixed effects only) and conditional $R^2_C$ (fixed and random effects) for each model.}
                \label{tab:proportion}                \footnotesize
                \begin{tabular}{c|c c | c c | c c | c c | c c |}
                & \multicolumn{2}{c|}{Intercept} & \multicolumn{2}{c|}{Proportion} & \multicolumn{2}{c|}{Disturbance} & \multicolumn{2}{c|}{Interaction} & \multicolumn{2}{c|}{$R^2$} \\
                Motif & $\beta$ & $p$ & $\beta$ & $p$ & $\beta$ & $p$ & $\beta$ & $p$ & $R^2_M$ & $R^2_C$ \\
                \hline
                3-sp Chain & 0.574 & \textless0.001 & -0.00508 & \textless0.001 & -0.139 & \textless0.001 & -0.00337 & \textless0.001 & 0.900 & 0.912 \\
                App. Com. & 0.574 & \textless0.001 & -0.00312 & \textless0.001 & -0.139 & \textless0.001 & 0.00410 & \textless0.001 & 0.900 & 0.911 \\
                Dir. Com. & 0.574 & \textless0.001 & 0.00564 & \textless0.001 & -0.139 & \textless0.001 & 0.000256 & \textless0.001 & 0.901 & 0.911 \\
                Omnivory & 0.574 & \textless0.001 & 0.00709 & \textless0.001 & -0.139 & \textless0.001 & -0.00198 & \textless0.001 & 0.894 & 0.912 \\
                \end{tabular}
            \end{table}

@@

            By fitting linear regressions of persistence against motif proportions for the species for each network separately, we can extract the slopes and analyze their distribution. This reveals information on how the relationship change with the level of disturbance and global network structure. For the global network parameters the network size had a much smaller effect than connectance (Fig.~\ref{fig:density_prop_S}; \emph{Appendix SZ})and therefore we here focus on only connectance.

            Networks with high connectance generally have more similar relationships between persistence and motif participation, i.e., sharper peaks of the density distributions (Fig.~\ref{fig:density_prop_C}). However, the interaction between a species' participation in the various motifs and disturbance changes with connectance  (Figure~\ref{fig:density_prop_C}).
            This is in particular evident for the direct competition and omnivory motif. At low and medium connectances there is little change in the proportion of positive slopes (\textgreater80\%) for the different levels of disturbance. However, at high connectances the proportion of positive slopes is overall lower and also decreases with increasing disturbance. This means that at low levels of connectance, in a majority of cases an increased proportion of the direct competition motif increase persistence, while the opposite is true with high connectance. 
            The trend is reversed for the omnivory motif.
            Overall, the proportion of networks showing a positive effect of omnivory decreases with increasing disturbance.
            This decrease is strongest at low and moderate connectances but very weak at high connectance. (Figure~\ref{fig:density_prop_C}). Notably, the distribution of slopes for the omnivory motif is wider (effect is more variable) the lower the connectance is.
            Hence, the level of connectance influence whether a high proportion of the omnivory motif is associated with higher persistence or not.

@@

        \begin{figure}[h!]
             \centering
             \includegraphics[width=\textwidth]{figures/prop_dens_bp_vs_S_allC.pdf}
            \caption{Density (y-axis) of slopes (x-axis) for all simulated webs of all sizes - a visualization of how an increased proportion of each motif (different colored lines) affects persistence of consumer species. The slopes are derived from standard linear regression. A negative slope value reflects a negative relationship between increased participation in a motif and persistence, while a positive slope value reflects a positive relationship - an increased proportion of a specific motif increase persistence. The fraction of replicates with a slope greater than zero are stated in numbers in each sub-plot, the color corresponding to motif (legend). Columns show the result for various disturbances on the basal level, from $\pi_{disturbed} = 0.1$ (left) to $\pi_{disturbed} = 0.5$ (right). Rows show various levels of network size. The vertical line indicate zero on the x-axis.}
            \label{fig:density_prop_S}
        \end{figure}

@@

        Persistence varies with both species in-degree and trophic level (Fig.~\ref{fig:motifs_vs_TL_and_deg}; \emph{Appendix SZZ}). Increased trophic level is associated with decreasing persistence, although the rate of this decline is slower at higher levels of disturbance (Table~\ref{tab:per_vs_TLdeg}).
        The interaction between in-degree and disturbance is even stronger, such as having a large number of prey is associated with higher persistence in the no disturbance scenario, but lower persistence at high disturbance.

        \begin{table}[hb!]
            \caption{Coeffcients ($\beta$) for regressions of consumers' probabilities of persistence against simple measures of species' role (STL or in-degree), level of disturbance to basal resources, and their interaction. Predictors were centered and scaled before model fitting. All $p$-values were \textless0.001. The level of disturbance is reflected by basal resources having a baseline probability of extinction ranging between $0.1 - 0.5$.}
            \label{tab:per_vs_TLdeg}
            \centering
            \begin{tabular}{l|c  c  c |}
                Simple role measure & Role & Disturbance & Interaction \\
                \hline
                STL & -0.0218 & -0.139 & 0.00508 \\
                in-degree & -0.00130 & -0.139 & -0.00908 \\
            \end{tabular}
        \end{table}

@@

        \subsubsection*{Motif participation and network size and connectance}

            \begin{table}[hb!]
            \centering
            \caption{The meso-scale composition of a network varies with size and connectance. Here we give the range and mean ($\pm$ standard deviation) proportion of each motif in species' motif participation vectors. 
            We also show the effects ($\beta$) of network size, connectance, and their interaction in linear models predicting the proportion of each motif in a participation vector.
            All effects were significant ($p$\textless0.001).
            Predictors were not centred or standardized before model fitting. Motifs are ordered according to mean proportion.}
            % Relevant lms are pchainlm, pomnilm, papplm, pdirlm}
            \label{tab:partic_vs_SC}   
            \footnotesize
            \begin{tabular}{c|c c c | c c c}
                Motif & Min & Max & Mean (SD) & Size & Connectance & Interaction \\
                \hline
                App. Comp & 0.250 & 0.765 & 0.422 (0.0645) & -5.06$\times10^{-4}$ & -1.00 & 2.59$\times10^{-3}$ \\
                Chain & 0.109 & 0.413 & 0.235 (0.042) & 1.78$\times10^{-4}$ & -0.157 & -3.27$\times10^{-3}$ \\
                Dir. Comp & 0.0501 & 0.359 & 0.179 (0.0407) & -3.56$\times10^{-5}$ & -0.556 & 5.92$\times10^{-3}$ \\
                Omnivory & 0.006 & 0.346 & 0.164 (0.0790) & 3.64$\times10^{-4}$ & 1.71 & -5.24$\times10^{-3}$ \\   
                \hline
                \end{tabular}
                \end{table}

        The numbers of different motifs in a network may vary with web size, connectance, and their interaction.
        To establish this context, we fit linear models relating the proportion of each motif in a species' role against network size, connectance, and their interaction.

        \subsubsection*{Motif participation and simple role measures}

            Species' motif roles also vary with their in-degree and trophic level (Fig.~\ref{fig:motifs_vs_TL_and_deg}).
            Species with higher in-degree tend to have higher proportions of their motif role made up by omnivory. Proportions of the other three motifs tend to decline with increasing degree.

@@

    [[Big deal result: connectance is important for motif structure of network, size not so much]]

    [[Persistence depends on S, C, interaction with $basal_p$ (lowest persistence swaps from highest S to lowest C in Figs. 1-2, high C in both cases - but small absolute differences so maybe we don't want to make too big a deal out of this)]]

    [[proportion of omnivory increases with increasing C, while the other doesn't. Connect to later findings involving omnivory]]

@@

        \begin{figure}
            \centering
            \includegraphics[width=.95\textwidth]{figures/persistence_positions_byprey.eps}
            \caption{A species' probability of persistence varied with the frequency of different motif positions in its role. Relationships are shown for the range 0-0.8 for all positions, but some positions (especially in the omnivory motif) are less common. Line colour indicates the motif containing a position. Line style indicates the number of prey within the motif for each position. Symbol shape indicates the number of predators within the motif for each position; note that only bottom-up extinctions were included in our simulations. The top set of lines corresponds to a probability of extinction for basal resources of 0.1. The middle set of lines correspons to a probability of extinction for basal resources of 0.26, and the lowest set of lines corresponds to a probability of extinction for basal resources of 0.5.}
            \label{fig:persistence_positions_prey}
        \end{figure}

@@

        [[have fit these models but no figure yet - seems like degree and the 2-prey positions show the same pattern so they're probably tightly linked. STL may explain the differences in top and middle positions for the chain. There's still a fair amount of differences among the 0 prey and 1 prey motifs though, so motifs still provide unique information that degree and STL don't.]]
